### 2025-05-08 futureWork/rlHedging.tex
final draft

The objective in an \gls{mdp} is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time.
A \gls{mdp} provides a mathematical framework for solving sequential decision-making tasks in an enviornment where outcomes are partly random and partly under the control of a hedging agent. 
For hedging \gls{va} contracts, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
In this section, we reformulate the hedging enviornment of \gls{va} contracts from Section~\ref{subsec:VApayout} as an \gls{mdp} and define the key components of the \gls{mdp}.

@@

At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
\begin{equation*}
    S_0=F_0=G_0.
\end{equation*}
At each time $t=1,\ldots,T$, the following events take place in the following order:
\begin{enumerate}
    \item The dynamic lapse rate $q_t$ is applied to the contract, i.e., $q$ of the policyholders leave the contract at time $t$.
        \begin{equation} \label{eq3:lapse}
            q_t = q_t^B \cdot \text{clip} (M_q (\frac{G_{t-1}}{F_{t-1}} - D_q), L_q, U_q),
        \end{equation}
    where $q_t^B$ is the base lapse rate, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, i.e.,
    $$
    \text{clip}(x, a, b) = \begin{cases}
        a, & \text{if } x < a \\
        x, & \text{if } a \leq x \leq b \\
        b, & \text{if } x > b,
    \end{cases}
    $$
    and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners’ Valuation Manual 21~\citep{naic2021}.
    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
        \begin{equation} \label{eq3:subaccount}
            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g)\cdot(1-q_t),
        \end{equation} 
    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.

@@

Consider a \gls{va} contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
The value of the hedge portfolio at time~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is the underlying stock price and any time $t>0$.
This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{-rt}.
\end{equation*}
Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The \gls{pl} of the \gls{va} contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
Mathematically, the present value of the liability for a \gls{gmmb} contract is 
\begin{align} \label{eq3:lossGMMB}
L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+  \nonumber \\ 
    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right) 
\end{align}
where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot |\Delta_t - \Delta_{t-1}|$ is the tranaction cost at time $t$~\citep{garleanu2013dynamic}.
Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
Similarly, the present value of the liability for a \gls{gmwb} contract is
\begin{equation} \label{eq3:lossGMWB}
L = \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right)
\end{equation}
The \gls{gmwb} payout is implicitly included in $F_t\eta_n$.
Both Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
The discrete-time hedging problem of \gls{va} contracts can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
Different from the formulation in Chapter~\ref{chap:project2}, the hedging weight $\Delta_0, \ldots, \Delta_{T-1}$ are not estimated from inner simulation steps but are directly controlled by a \gls{drl} agent.
Thus, the hedging weight $\Delta_t$ at time $t$ is estimated using a neural network whose input is the state $\mathbf{s}_t$ and output is $\Delta_t$.

@@

\section{Exising RL Algorithms and Their Limitations} \label{sec:RLAlgorithms}

\subsection{Model-Based RL: From AlphaZero to Deep Hedging}
\gls{drl} first attacted attentions when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
Soon after, AlphaZero~\citep{silver2016mastering} emerged as a model-based \gls{rl} algorithm that improves over self-plays.
It quickly extended beyond Go to other games like Chess and Shogi.
In essence, the AlphaZero agent use a neural network to paramaterize the policy and the value function.
The neural network takes the current state of the game as input and outputs the probability distribution of the next move and a value of the current state.
\begin{equation}
    (\mathbf{\pi}, v) = f_{\theta}(s), \quad L(\theta) = - \mathbf{\pi}^{\intercal} \log(\mathbf{p}) + (z - v)^2  + c||\theta||^2,
\end{equation}
where $f_{\theta}$ is a neural network with parameters $\theta$, $s$ is a current state of the game, $\pi$ is a policy, $v$ is a value of the current state, and $c$ is a regularization parameter.
$\mathbf{p}$ and $z$ are a probability distribution of the next move and an outcome of the game, respectively.
They are induced by a planning algorithm, i.e., \gls{mcts}.
Since it is infeasible to efficiently simulate trajectories in the game of Go, a planning algorithm is necessary to generate expected outcomes.
The neural network $f_{\theta}$ is trained with a stochastic gradient descent algorithm to minimize $L$.
$L$ has three components.
The last term penalizes large neural network weights.
Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the \gls{mcts}.
The neural network is trained to fit the planned outcomes of the game.
It stores a global solution that predicts the outcome of the game and the next move before they are actually observed.
This is known as model-based \gls{rl}~\citep{sutton2018reinforcement}.
Using a model allows for planning, i.e., decision-making take place using future situations that have not been experienced by the agent.

In a typical hedging problem, the transition probabilities are independent from the hedging weights, i.e., the actions.
This simplifies the planning as complete trajectories can be simulated without the need of a planning algorithm.
In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses monte carlo simulations to generate sample paths of asset dynamics.
These simulations are conducted based on predefined stochastic asset models. 
The parameters and structure of these models are specified in advance, dictating the behavior of the simulated asset prices.

@@

Boardly speaking, model-free \gls{rl} can be categorized into two types: value-based \gls{rl} and policy-based \gls{rl}.
Value-based approaches learn the value function directly from the data and derive the policy from the learned value function. 
The value function is learned by training a \gls{dnn} to approximate the value function, which quantifies the expected cumulative reward over time. 
The policy is then derived from the learned value function by selecting the action that maximizes the value function at each state. 
~\cite{mnih2015human} is the first paper to demonstrate the effectiveness of value-based \gls{drl} in training agents to play Atari games.
To update the value function, the \gls{dnn} is trained to minimize the difference between the current value function and the target value function, which is updated based on the maximum expected reward from the previous iteration.
When trained to approximate the value function, the \gls{dnn} benefits from the use of experience replay buffers, which is proposed by~\cite{lin1992self} to store and sample historical transitions and uniformly sampled during training to enhance the sample efficiency and stability of the learning process.
~\cite{kolm2019dynamic} uses a value-based \gls{drl} approach to hedge European options under the \gls{gbm} asset model.

@@

\begin{algorithm}
    \caption{Recurrent \gls{ppo} with \gls{lstm} for Hedging Variable Annuities} 
    \begin{algorithmic}[1] \label{alg3:ppoHedging-rnn}
        \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
        \STATE  Initialize the \gls{lstm} layers with random weights, and set the hidden state $h_0$ to zeros.
        \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
        \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
        \STATE  \quad Reset the \gls{lstm} hidden state $h_0$ to zeros at the beginning of each trajectory.
        \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(\mathbf{s}_t, a_t)$ using value function $V_{\phi_k}$.
        \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
        \begin{equation*}
            \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t)  \right\} \right]
        \end{equation*}
        \STATE  \quad Update the value function parameters $\phi_{k+1}$ by minimizing the mean squared error between the predicted value and the actual collected reward.
        \begin{equation*}
            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(\mathbf{s}_t) - \hat{R}_t \right)^2
        \end{equation*}
        \STATE  \textbf{End For}
    \end{algorithmic}
\end{algorithm}

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/tikz/ppo_diagram.pdf}
        \caption{regular \gls{ppo}}
        \label{subfig3:architecturePPO}
    \end{subfigure}
    \hspace{1cm}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/tikz/recurrentppo_diagram.pdf}
        \caption{Recurrent \gls{ppo} with \gls{lstm}}
        \label{subfig3:architectureLSTMPPO}
    \end{subfigure}
    \caption{\gls{ppo} Network Architectures} 
    \label{fig3:architecturePPO}
\end{figure}

@@

\begin{table}[ht!]
    \centering
    \begin{tabular}{ll} 
        \toprule
        Hyperparameter      & Value \\
        \midrule
        $|\mathcal{D}_k|$   & 16        \\
        $\epsilon$          & 0.2       \\
        Learning rate       & 0.0001    \\
        $S_0$               & 1000      \\
        $\mu$               & 0.00375   \\
        $\sigma$            & 0.0457627 \\
        $r$                 & 0.002     \\
        $T$                 & 240       \\
        \bottomrule
    \end{tabular}
    \caption{Model hyperparameters and \gls{gmmb} contract specifications} 
    \label{tab3:hyperparameters}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{./futureWork/figures/CVaR_histories.png}
    \caption{Hedging performance of deep hedging with \gls{tl}}
    \label{fig3:dh-transfers}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{./futureWork/figures/PPO_DH.png}
    \caption{Hedging performance of recurrent \gls{ppo} and deep hedging}
    \label{fig3:ppo_dh}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBM.png}
        \caption{\gls{gbm}}
    \end{subfigure}
    \hspace{1cm}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBMRS.png}
        \caption{\gls{rsgbm}}
    \end{subfigure}
    \caption{Hedging performance of standard \gls{ppo} and recurrent \gls{ppo}} 
    \label{fig3:ppo_result}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/figures/PPO_cost_001.png}
        \caption{$C = 0.001$}
    \end{subfigure}
    \hspace{1cm}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/figures/PPO_cost_02.png}
        \caption{$C = 0.02$}
    \end{subfigure}
    \caption{Hedging performance of recurrent \gls{ppo} and delta hedging with different transaction costs} 
    \label{fig3:ppo_cost}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{./futureWork/figures/PPO_anchor.png}
    \caption{Hedging performance of recurrent \gls{ppo} with or without anchor}
    \label{fig3:ppo_anchor}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{./futureWork/figures/PPO_GMWB.png}
    \caption{Hedging performance of recurrent \gls{ppo} with \gls{gmwb}}
    \label{fig3:ppo_GMWB}
\end{figure}

>>>>

The objective in an \gls{mdp} is to find a policy, $\pi: \mathcal{S} \rightarrow \mathbb{P}(\mathcal{A})$, that maximizes the cumulative reward over time.
A \gls{mdp} provides a mathematical framework for solving sequential decision-making tasks in an environment where outcomes are partly random and partly under the control of a hedging agent. 
For hedging \gls{va} contracts, the asset dynamics and the mortality model are not controlled by the agent, but the agent controls the cumulative reward by deciding on the hedging weights.
In this section, we reformulate the hedging environment of \gls{va} contracts from Section~\ref{subsec:VApayout} as an \gls{mdp} and define the key components of the \gls{mdp}.

@@

At the inception of the contract, i.e., $t=0$, we assume that the whole premium is invested in the stock index and the guarantee base is set to the sub-account value:
\begin{equation*}
    S_0=F_0=G_0.
\end{equation*}
At each time $t=1,\ldots,T$, the following events take place in the following order:
\begin{enumerate}
    \item The dynamic lapse rate $q_t$ is applied to the contract, i.e., $q$ of the policyholders leave the contract at time $t$.
        \begin{equation} \label{eq3:lapse}
            q_t = q_t^B \cdot \text{clip} (M_q (\frac{G_{t-1}}{F_{t-1}} - D_q), L_q, U_q),
        \end{equation}
    where $q_t^B$ is the base lapse rate, $\text{clip}(x, a, b)$ is a function that clips the value of $x$ to be within the range $[a, b]$, i.e.,
    $$
    \text{clip}(x, a, b) = \begin{cases}
        a, & \text{if } x < a \\
        x, & \text{if } a \leq x \leq b \\
        b, & \text{if } x > b,
    \end{cases}
    $$
    and $M_q$, $D_q$, $L_q$, and $U_q$ are the model parameters taken from National Association of Insurance Commissioners' Valuation Manual 21~\citep{naic2021}.
    \item The sub-account value changes according to the growth of the underlying stock and the (gross) management fee is deducted. That is, 
        \begin{equation} \label{eq3:subaccount}
            F_t = F_{(t-1)_+}\cdot\frac{S_{t}}{S_{t-1}}\cdot(1-\eta_g)\cdot(1-q_t),
        \end{equation} 
    where $(x)^+=\max\{x,0\}$ and $F_{(t-1)_+}$ will be defined later. The insurer's income at time $t$ is the net management fee, i.e., $F_t\eta_n$.

@@

Consider a \gls{va} contract whose delta hedge portfolio at any time~$t$, $t=0,1,\ldots,T-1$, consists of $\Delta_t$ units in the underlying stock and $B_t$ amount of a risk-free zero-coupon bond maturing at time $T$.
The value of the hedge portfolio at time~$(t-1)$ is:
\begin{equation*}
    H_{t-1} = \Delta_{t-1} S_{t-1} + B_{t-1},
\end{equation*}
where $S_t$ is the underlying stock price and any time $t>0$.
This hedge portfolio is brought forward to the next rebalancing time~$t$, when its value becomes:
\begin{equation*}
    H_{t}^{bf} = \Delta_{t-1} S_{t} + B_{t-1}e^{-rt}.
\end{equation*}
Therefore, the time~$t$ hedging error, i.e., the cash flow incurred by the insurer due to rebalancing at time~$t$, is
\begin{equation}
    HE_t = H_t - H^{bf}_t, \quad t=1,\ldots, T-1.
\end{equation}
The \gls{pl} of the \gls{va} contract includes the cost of the initial hedge ($H_0$), the hedging errors~\eqref{eq2:hedgingerror}, the unwinding of the hedge at maturity ($H^{bf}_T$), and the contract payout at time~$t\in \{0,\ldots,T\}$.
Mathematically, the present value of the liability for a \gls{gmmb} contract is 
\begin{align} \label{eq3:lossGMMB}
L   & = H_0 - e^{-rT} H^{bf}_T + \sum_{t=1}^{T-1} e^{-rt} HE_t + \sum_{t=1}^T e^{-rt} C_t - \sum_{t=1}^T e^{-rt} F_t\eta_n + e^{-rT} (G_t - F_t)^+  \nonumber \\ 
    & = e^{-rT} (G_T - F_{T^+})^+ + \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right) 
\end{align}
where the equality holds by a rearrangement of terms and a telescopic sum simplification of $e^{-rt}B_t$, $t=0,\ldots,T-1$, and $C_t := C \cdot S_{t-1} \cdot |\Delta_t - \Delta_{t-1}|$ is the transaction cost at time $t$~\citep{garleanu2013dynamic}.
Hence, the present liability consist of the hedging errors, the transaction costs, the net management fees, and the contract payouts.
Similarly, the present value of the liability for a \gls{gmwb} contract is
\begin{equation} \label{eq3:lossGMWB}
L = \sum_{t=1}^T e^{-rt}  \left( \Delta_{t-1} (S_{t-1} - e^{-r} S_t) + C_t - F_t\eta_n \right)
\end{equation}
The \gls{gmwb} payout is implicitly included in $F_t\eta_n$.
Both Equation~\eqref{eq3:lossGMMB} and Equation~\eqref{eq3:lossGMWB} neglect the transaction cost to liquidate the hedge portfolio at maturity.
The discrete-time hedging problem of \gls{va} contracts can be conveniently formulated as an \gls{mdp}, where the states, actions, transition probabilities, policies, and rewards are defined as follows.
Different from the formulation in Chapter~\ref{chap:project2}, the hedging weight $\Delta_0, \ldots, \Delta_{T-1}$ are not estimated from inner simulation steps but are directly controlled by a \gls{drl} agent.
Thus, the hedging weight $\Delta_t$ at time $t$ is estimated using a neural network whose input is the state $\mathbf{s}_t$ and output is $\Delta_t$.

@@

\section{Existing RL Algorithms and Their Limitations} \label{sec:RLAlgorithms}

\subsection{Model-Based RL: From AlphaZero to Deep Hedging}
\gls{drl} first attracted attention when AlphaGo~\citep{silver2016mastering} surpasses human in playing Go. 
Soon after, AlphaZero~\citep{silver2016mastering} emerged as a model-based \gls{rl} algorithm that improves over self-plays.
It quickly extended beyond Go to other games like Chess and Shogi.
In essence, the AlphaZero agent use a neural network to parameterize the policy and the value function.
The neural network takes the current state of the game as input and outputs the probability distribution of the next move and a value of the current state.
\begin{equation}
    (\mathbf{\pi}, v) = f_{\theta}(s), \quad L(\theta) = - \mathbf{\pi}^{\intercal} \log(\mathbf{p}) + (z - v)^2  + c||\theta||^2,
\end{equation}
where $f_{\theta}$ is a neural network with parameters $\theta$, $s$ is a current state of the game, $\pi$ is a policy, $v$ is a value of the current state, and $c$ is a regularization parameter.
$\mathbf{p}$ and $z$ are a probability distribution of the next move and an outcome of the game, respectively.
They are induced by a planning algorithm, i.e., \gls{mcts}.
Since it is infeasible to efficiently simulate trajectories in the game of Go, a planning algorithm is necessary to generate expected outcomes.
The neural network $f_{\theta}$ is trained with a stochastic gradient descent algorithm to minimize $L$.
$L$ has three components.
The last term penalizes large neural network weights.
Its first two terms measure the similarity between $f_{\theta}(s)$, the learned policy and value function, with the action and game outcome planned by the \gls{mcts}.
The neural network is trained to fit the planned outcomes of the game.
It stores a global solution that predicts the outcome of the game and the next move before they are actually observed.
This is known as model-based \gls{rl}~\citep{sutton2018reinforcement}.
Using a model allows for planning, i.e., decision-making take place using future situations that have not been experienced by the agent.

In a typical hedging problem, the transition probabilities are independent from the hedging weights, i.e., the actions.
This simplifies the planning as complete trajectories can be simulated without the need of a planning algorithm.
In contrast to AlphaZero, deep hedging~\citep{buehler2019deep} uses \gls{mc} simulations to generate sample paths of asset dynamics.
These simulations are conducted based on predefined stochastic asset models. 
The parameters and structure of these models are specified in advance, dictating the behavior of the simulated asset prices.

@@

Broadly speaking, model-free \gls{rl} can be categorized into two types: value-based \gls{rl} and policy-based \gls{rl}.
Value-based approaches learn the value function directly from the data and derive the policy from the learned value function. 
The value function is learned by training a \gls{dnn} to approximate the value function, which quantifies the expected cumulative reward over time. 
The policy is then derived from the learned value function by selecting the action that maximizes the value function at each state. 
~\cite{mnih2015human} is the first paper to demonstrate the effectiveness of value-based \gls{drl} in training agents to play Atari games.
To update the value function, the \gls{dnn} is trained to minimize the difference between the current value function and the target value function, which is updated based on the maximum expected reward from the previous iteration.
When trained to approximate the value function, the \gls{dnn} benefits from the use of experience replay buffers, which is proposed by~\cite{lin1992self} to store and sample historical transitions and uniformly sampled during training to enhance the sample efficiency and stability of the learning process.
~\cite{kolm2019dynamic} uses a value-based \gls{drl} approach to hedge European options under the \gls{gbm} asset model.

@@

\begin{algorithm}
    \caption{Recurrent PPO with LSTM for Hedging Variable Annuities} 
    \begin{algorithmic}[1] \label{alg3:ppoHedging-rnn}
        \STATE  Initialize policy parameters $\theta_0$ and value function parameters $\phi_0$.
        \STATE  Initialize the \gls{lstm} layers with random weights, and set the hidden state $h_0$ to zeros.
        \STATE  \textbf{For} {iteration $k=0, 1,2,\ldots$} \textbf{do}
        \STATE  \quad Collect a set of trajectories $\mathcal{D}_k$ by sampling from the environment with policy $\pi_{\theta_{k}}$.
        \STATE  \quad Reset the \gls{lstm} hidden state $h_0$ to zeros at the beginning of each trajectory.
        \STATE  \quad Compute the rewards $\hat{R}_t$ for each trajectory in $\mathcal{D}_k$.
        \STATE  \quad Estimates the advantage function with $\hat{A}_{\pi_{\theta_k}}(\mathbf{s}_t, a_t)$ using value function $V_{\phi_k}$.
        \STATE  \quad Update the policy parameters $\theta_{k+1}$ by 
        \begin{equation*}
            \max_{\theta} \mathbb{E}\left[ \min \left\{ \Lambda_t(\theta)\hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t), \text{clip}(\Lambda_t(\theta), 1-\epsilon, 1 + \epsilon) \hat{A}^{\pi_{\theta}}(\mathbf{s}_t, a_t)  \right\} \right]
        \end{equation*}
        \STATE  \quad Update the value function parameters $\phi_{k+1}$ by minimizing the mean squared error between the predicted value and the actual collected reward.
        \begin{equation*}
            \phi_{k+1} = \arg \min_{\phi} \frac{1}{|\mathcal{D}_k|T} \sum_{\mathcal{\kappa} \in \mathcal{D}_k} \sum_{t=0}^{T} \left( V_{\phi}(\mathbf{s}_t) - \hat{R}_t \right)^2
        \end{equation*}
        \STATE  \textbf{End For}
    \end{algorithmic}
\end{algorithm}

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/tikz/ppo_diagram.pdf}
        \caption{Regular PPO}
        \label{subfig3:architecturePPO}
    \end{subfigure}
    \hspace{1cm}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/tikz/recurrentppo_diagram.pdf}
        \caption{Recurrent PPO with LSTM}
        \label{subfig3:architectureLSTMPPO}
    \end{subfigure}
    \caption{PPO Network Architectures} 
    \label{fig3:architecturePPO}
\end{figure}

@@

\begin{table}[ht!]
    \centering
    \begin{tabular}{ll} 
        \toprule
        Hyperparameter      & Value \\
        \midrule
        $|\mathcal{D}_k|$   & 16        \\
        $\epsilon$          & 0.2       \\
        Learning rate       & 0.0001    \\
        $S_0$               & 1000      \\
        $\mu$               & 0.00375   \\
        $\sigma$            & 0.0457627 \\
        $r$                 & 0.002     \\
        $T$                 & 240       \\
        \bottomrule
    \end{tabular}
    \caption{Model hyperparameters and GMMB contract specifications} 
    \label{tab3:hyperparameters}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{./futureWork/figures/CVaR_histories.png}
    \caption{Hedging performance of deep hedging with TL}
    \label{fig3:dh-transfers}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.5\textwidth]{./futureWork/figures/PPO_DH.png}
    \caption{Hedging performance of recurrent PPO and deep hedging}
    \label{fig3:ppo_dh}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBM.png}
        \caption{GBM}
    \end{subfigure}
    \hspace{1cm}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/figures/PPOs_GBMRS.png}
        \caption{RS-GBM}
    \end{subfigure}
    \caption{Hedging performance of standard PPO and recurrent PPO} 
    \label{fig3:ppo_result}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/figures/PPO_cost_001.png}
        \caption{$C = 0.001$}
    \end{subfigure}
    \hspace{1cm}
    \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{./futureWork/figures/PPO_cost_02.png}
        \caption{$C = 0.02$}
    \end{subfigure}
    \caption{Hedging performance of recurrent PPO and delta hedging with different transaction costs} 
    \label{fig3:ppo_cost}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{./futureWork/figures/PPO_anchor.png}
    \caption{Hedging performance of recurrent PPO with or without anchor}
    \label{fig3:ppo_anchor}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\textwidth]{./futureWork/figures/PPO_GMWB.png}
    \caption{Hedging performance of recurrent PPO with GMWB}
    \label{fig3:ppo_GMWB}
\end{figure}
